To address the previous research question, this master's 
thesis is structured into eight steps, as shown in Figure \ref{fig:roadmap}.

\subsection*{Preliminary Thermodynamic Program}

In this first part, a classical heat pump cycle will be modeled numerically. Each student will work 
simultaneously on different components, such as a semi-empirical model for the compressor 
or a moving-boundary model for the heat exchangers. The cycle analysis will include 
both energy and exergy analyses to ensure optimal performance. The numerical model will be developed in 
\texttt{Python}, using the \texttt{CoolProp} library to access thermodynamic property data.

\subsection*{Final Thermodynamic Program}

%First, various cycle configurations 
%will be optimized to determine the widest possible operating range. Then, the program will be generalized 
%to improve its robustness and flexibility.

First, various cycle configurations will be optimized to determine their own optimal components. 
Then, the program will be generalized to improve its robustness and flexibility.



\subsection*{Sizing of the Main Components and P\&ID}

%After defining the operating range, the main components, such as heat exchangers and expansion valves, 
%will be selected. 

After defining the optimal components, a trade-off analysis will be conducted to select 
the final components of the machine. Simulations will be performed to ensure that the 
system can operate in all configurations. A P\&ID (Piping and Instrumentation Diagram) will also be created to illustrate the 
system layout and control strategies.

\subsection*{Development of an Initial Control Strategy}

One of the main advantages of this machine lies in its ability to simulate different operating conditions 
thanks to the dual evaporator. Therefore, a suitable control logic must be implemented. This step is crucial 
for determining the appropriate type and placement of sensors.

\subsection*{CAD and Operational Model}

In this section, the mechanical design of the machine will be carried out. 
This includes material and component selection, the design of heat exchangers and insulation, and 
the creation of detailed technical drawings. The resulting operational model 
will also serve to analyze the machine’s dynamic behavior.

\subsection*{Prototype Construction and Instrumentation}

This stage involves constructing the prototype and installing the necessary instrumentation.

\subsection*{Safety Validation of the Prototype}

Before testing, the prototype will be 
validated by the CREDEM platform to ensure compliance with safety requirements.

\subsection*{Control Logic and Performance Validation}

Finally, the last stage will focus on evaluating the machine and its control logic. 
A series of tests will be conducted to verify proper operation and to collect data for 
comparison with theoretical predictions.
