Taking the different steps of the project presented in the previous section, 
the workload will be shared as follows:

\begin{enumerate}
\item \textbf{Preliminary Thermodynamic Program:} The EPL students will work 
in parallel on different sub-parts of the \texttt{Python} code, but strategic 
design decisions will be made jointly and mutual support will be provided as needed.
\item \textbf{Final Thermodynamic Program:} The optimization stategy for each configuration will be 
jointly developed by the EPL students to maximize the performance of the system in 
nominal conditions.
\item \textbf{Sizing of the Main Components and P\&ID:} Similar to the first phase, 
the EPL students will work in parallel on different components to maximize 
productivity, as this phase must be completed by the end of the first semester 
to ensure availability of the components for the prototyping phase.
\item \textbf{Establishment of a First Control Strategy:} All students will participate in the
development of a first control strategy for the prototype.
\item \textbf{CAD and Operational Model:} The ECAM student will lead the CAD work, 
with technical support from a CREDEM platform technician. The resulting Operational 
Model will be validated by the EPL students based on their initial thermodynamic design.
\item \textbf{Prototype Construction and Instrumentation:} The prototype will be built 
under the supervision of a CREDEM technician.
\item \textbf{Safety Validation of the Prototype:} This step will be fully managed 
by the CREDEM platform.
\item \textbf{Control Logic and Performance Validation:} Once the prototype is 
operational, the students will carry out the validation of control logic and 
performance, as well as fine-tune the prototype to optimize its operation.
\end{enumerate}

\noindent Throughout the project, weekly meetings will be organized between 
the students to discuss progress, share knowledge, and make important decisions. 
In addition, students will meet regularly with their mentors to present key results, 
receive feedback, and discuss challenges. Progress will also be reported formally 
during monthly meetings with the supervisor.